Sampling-Based Motion Planning for Tracking Evolution of Dynamic Tunnels in Molecular Dynamics Simulations

### 2017-10-31 paper.tex
didn't -> did not

The number of frames where dynamic tunnels were detected is summarized in Tab.~\ref{tab::dyn}.
In 2,860 frames, no static tunnel was found by CAVER, but  in 1,027 of these cases, a dynamic tunnel was detected and
in other 725 frames, a part of the tunnel (cavity) was detected.
The total number of frames where either end of a dynamic tunnel was detected or a cavity that is part of a dynamic tunnel was
1,197.
This shows that the proposed dynamic tunnel detection can bring new information about 1,197 of tunnels, that would be 
discarded in the analysis based solely on static tunnels.
No static tunnel was identified by the proposed method in frames, where no static tunnels were detected by CAVER.
As the positions of active site were taken from CAVER, which didn't find suitable place for the large probe in these frames,
also our algorithm could not detect any static tunnels there.
However, our method was able to track evolution of the dynamic tunnels in these frames.
No dynamic neither static tunnel was identified in 1,833 frames and therefore, behavior in these frames  remains unknown.
The results also show that no static tunnel was identified in 669 frames by the proposed method, while CAVER detected static tunnels there.
%The number of frames where the dynamic tunnels were detected is summarized in Tab.~\ref{tab::dyn}.
%In 2,860 frames, no static tunnel was found by CAVER, but in 1,027 frames of this set, a dynamic tunnel was detected.
%Both static and dynamic tunnels were detected in 1,324 frames.
%These results bring new information about the protein behavior. 
%They show that a path connecting the protein surface with the active site is more frequent than the static tunnels suggest.
%The examples of frames without a static tunnel, but containing a dynamic one, are depicted in Fig.~\ref{fig::seq1}.
%
%
%In the case of 3,816 frames where a static tunnel was detected by CAVER, no dynamic tunnel was detected by the proposed method. 
%3,118 frames out of 3,816 were identified as static.
%This indicates that some tunnels were detected as dynamic instead of static.
The proposed method is non-deterministic and it may happen, that some part of the tree does not reach the outer region of the protein and consequently, some exit points are not detected, which decreases the number of detected static tunnels.
These missed exit points are then reached in the next frame which leads to the detection of the dynamic tunnel.
The number of correctly classified static tunnels can be increased by using higher $\Imax$.
In our experiment, $\Imax=1,200$ was used with a lower value in order to process the whole sequence of 8,000 frames in a reasonable time.

>>>>

The number of frames where dynamic tunnels were detected is summarized in Tab.~\ref{tab::dyn}.
In 2,860 frames, no static tunnel was found by CAVER, but  in 1,027 of these cases, a dynamic tunnel was detected and
in other 725 frames, a part of the tunnel (cavity) was detected.
The total number of frames where either end of a dynamic tunnel was detected or a cavity that is part of a dynamic tunnel was
1,197.
This shows that the proposed dynamic tunnel detection can bring new information about 1,197 of tunnels, that would be 
discarded in the analysis based solely on static tunnels.
No static tunnel was identified by the proposed method in frames, where no static tunnels were detected by CAVER.
As the positions of active site were taken from CAVER, which did not find a suitable place for the large probe in these frames,
also our algorithm could not detect any static tunnels there.
However, our method was able to track evolution of the dynamic tunnels in these frames.
No dynamic neither static tunnel was identified in 1,833 frames and therefore, behavior in these frames  remains unknown.
The results also show that no static tunnel was identified in 669 frames by the proposed method, while CAVER detected static tunnels there.
%The number of frames where the dynamic tunnels were detected is summarized in Tab.~\ref{tab::dyn}.
%In 2,860 frames, no static tunnel was found by CAVER, but in 1,027 frames of this set, a dynamic tunnel was detected.
%Both static and dynamic tunnels were detected in 1,324 frames.
%These results bring new information about the protein behavior. 
%They show that a path connecting the protein surface with the active site is more frequent than the static tunnels suggest.
%The examples of frames without a static tunnel, but containing a dynamic one, are depicted in Fig.~\ref{fig::seq1}.
%
%
%In the case of 3,816 frames where a static tunnel was detected by CAVER, no dynamic tunnel was detected by the proposed method. 
%3,118 frames out of 3,816 were identified as static.
%This indicates that some tunnels were detected as dynamic instead of static.
The proposed method is non-deterministic and it may happen, that some part of the tree does not reach the outer region of the protein and consequently, some exit points are not detected, which decreases the number of detected static tunnels.
These missed exit points are then reached in the next frame which leads to the detection of the dynamic tunnel.
The number of correctly classified static tunnels can be increased by using higher $\Imax$.
In our experiment, $\Imax=1,200$ was used with a lower value in order to process the whole sequence of 8,000 frames in a reasonable time.
